---
title: "main-functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{main-functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
quantile_table(lower_quantile, upper_quantile)
```
This function should make a summary table that divides the GDP data into countries with Low GDP, Middle GDP, and High GDP based on what the user wants to classify each group as in relation to the rest of the data. It will display the total plastic waste for each GDP category, as well as the average GDP per capita for each individual category.

```{r}
sankey_plot(top_x_countries, top_x_companies)
```
This function should take in inputs of the number of top countries and top companies that we want to see displayed, and then display a Sankey diagram showing the flow of plastics between those countries and companies. 

```{r}
gdp_plastics_table(top_x_countries)
```
This function should take in an input of the top countries that we want displayed on the summary table, and it should output the countries, the amount of plastic waste they have, and their average GDP per capita.
