---
title: "main-functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{main-functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
quantile_table(
  lower_quantile = 0.33,
  upper_quantile = 0.66
)
```
This function creates a summary table that divides countries into Low GDP, Mid GDP, and High GDP groups using the 33rd and 66th percentiles of GDP per capita. The output shows total plastic waste, average GDP per capita, and each group’s share of total plastic waste.

```{r}
sankey_plot(
  top_x_countries = 5,
  top_x_companies = 10
)
```
This function creates a Sankey diagram showing the flow of plastic waste between the top 5 countries and top 10 companies. The countries and companies are selected based on total plastic waste, and the flows are colored by plastic type.

```{r}
gdp_plastics_table(
  top_x_countries = 5
)
```
This function creates a summary table for the top 5 countries with the highest plastic waste. The output includes each country’s total plastic waste and average GDP per capita.
